Results (Julia)

### 2025-04-03 notebooks/01_results_julia.qmd
figure: polish

```{julia}
using DrWatson
using Discontinuity
using AlgebraOfGraphics
using DataFramesMeta
@quickactivate
include("../src/main.jl");
M = var_mapping()

@@

```{julia}
maps1 = [M.l_log M.l_norm_log; M.j_log M.j_norm_log]
maps2 = [M.density_log M.B_log; beta_map M.bm0_log];
```

@@

let df = wind_df, fnames = ["wind_distribution_time", "wind_sw_paramters"]
    fs = temp_plot(df).([maps1, maps2])
    easy_save.(fnames, fs)
    display.(fs)
end
```

```{julia}
# let df = j_events_taus
let df = jno_df, color = r_map, fnames = ["juno_distribution_r", "juno_sw_paramters"]
    fs = temp_plot(df; color).([maps1, maps2])
    easy_save.(fnames, fs)
    display.(fs)
end
```

@@

>>>>

```{julia}
using DrWatson
using Discontinuity
using AlgebraOfGraphics
using DataFramesMeta
using Beforerr
@quickactivate
include("../src/main.jl");
M = var_mapping(; log_str="")

@@

```{julia}
maps1 = [M.l_log M.l_norm_log; M.j_log M.j_norm_log]
maps2 = [M.density_log M.B_log; M.beta M.bm0_log];
```

```{julia}
figure = (; size=Beforerr.figsize(7))

"""
    Strip trailing zeros from decimal numbers
"""
function _round(v;kw...)
    rounded = string(round(v; digits=1, kw...))
    # If it contains a decimal point, remove trailing zeros
    if contains(rounded, ".")
        # Remove trailing zeros
        rounded = replace(rounded, r"\.?0+$" => "")
        # If we removed everything after the decimal point, remove the decimal point too
        rounded = replace(rounded, r"\.$" => "")
    end
    return rounded
end

axis = (; 
    xticks = WilkinsonTicks(5),
    xtickformat = values -> [L"10^{%$(_round(v))}" for v in values],
    yscale=log10,
)
```

@@

let df = wind_df, fnames = ["wind_distribution_time", "wind_sw_paramters"]
    spec = data(df) * mapping(color=year_map)
    fs = map([maps1, maps2]) do m
        plot_dist(spec, m; 
            datalimits=datalimits_f,
            axis,
            figure
        )
    end
    easy_save.(fnames, fs)
    display.(fs)
end
```

![](../figures/wind_distribution_time.png)

![](../figures/wind_sw_paramters.png)

```{julia}
# let df = j_events_taus
let df = jno_df, color = r_map, fnames = ["juno_distribution_r", "juno_sw_paramters"]
    spec = data(df) * mapping(; color)
    fs = map([maps1, maps2]) do m
        plot_dist(spec, m; 
            datalimits=datalimits_f,
            axis,
            figure
        )
    end
    resize_to_layout!.(fs)
    easy_save.(fnames, fs)
    display.(fs)
end
```

![](../figures/juno_distribution_r.png)
![](../figures/juno_sw_paramters.png)

@@

## Magnetic field magnitude and radial dependency

```{julia}
rfunc(r) = sqrt(1/r^2 + 1/r^4)
rfunc(B,r) = B / rfunc(r)
B_r_scaled= (:"B.mean", :r) => (log10 ∘ rfunc)
B_m0_scaled= (:"fit.vars.amplitude", :r)  => (log10 ∘ abs ∘ rfunc)
let df = jno_df, color = r_map, m = [M.B_log M.bm0_log; B_r_scaled B_m0_scaled]
    spec = data(df) * mapping(; color)
    f = plot_dist(spec, m; 
            datalimits=datalimits_f,
            axis
        )
    display(f)
end
```
